---
title: "Who Represents You?"
output:
  html_document: default
css: styles.css
---




```{r init, include=FALSE}
source("keys.R")
## you may also load necessary libraries and set various options here
library(dplyr)
library(httr)
library(jsonlite)
library(stringr)
library(knitr)
knitr::opts_chunk$set(error=TRUE)
                           # continue compiling on error
```

```{r address, include=FALSE}
## insert your address here.  It does not to have quite complete.
## Test your code with addresses in different states, see if it works
address <- "4535 12th Ave NE, Seattlem WA, 98105"
```

```{r processData, include=FALSE}
## Make the main computations here.  Keep the functions in a separate file(s)
## and only include the final operations here.
## You have to 'source()' your main R file(s) here:
source('process_data.R')
## You may also have to do some additional processing here
```

## Your Representatives

This is a report about the political representatives for residents of *Seattle*, **WA**. All the data was extracted 
from [Propublica API]("https://projects.propublica.org/api-docs/congress-api/members/#members"), and [Google Civic Platform]("https://developers.google.com/civic-information/docs/v2/representatives"). Below is the brief table for the political representatives for the 
given address.


```{r table, echo=FALSE}
## You may want to print the table in a nice way using `knitr::kable()`
## when you have already created it.
knitr::kable(final.table)
```

## House of Representatives

```{r graph, echo=FALSE}
##
ggplot(data = representatives) +
  geom_bar(mapping = aes(x = representatives$party, fill = party)) +
  ggtitle("Party Affiliation of the Representatives") +
  labs(x = "party", y = "# of Representatives") +
  scale_fill_manual(values = c("red", "blue")) +
  coord_flip()

ggplot(data = representatives) +
  geom_bar(mapping = aes(x = representatives$gender, fill = gender)) +
  ggtitle("Gender Distribution of the Representatives") +
  labs(x = "gender", y = "# of Representatives") +
  coord_flip()
```


## **`r name`**

Here is a more in-depth information about a specific representative, *`r name`*. The representative is a **`r rep.party`**, `r age` years old, and you can find their twitter on [`r twitter`](paste("www.twitter.com/", twitter)). Fun fact, of the last 20 congressional votes, the representative was in accordance with the majority `r votes.percentage` of the time.


